```latex
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}

\geometry{a4paper, margin=2cm}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{Page \thepage}

\begin{document}

% First Page - Exam Cover Sheet
\begin{center}
{\large \textbf{OCR A-LEVEL COMPUTER SCIENCE}}

\vspace{1cm}

{\Large \textbf{H446/01 Computer Systems}}

\vspace{1cm}

\begin{tabular}{|p{0.45\textwidth}|p{0.45\textwidth}|}
\hline
Candidate Name: & Center Number: \\
& \\
\hline
Candidate Number: & Date of Examination: \\
& \\
\hline
\end{tabular}

\vspace{1cm}

\begin{itemize}
\item[] Total Marks: 40
\item[] Time Allowed: 1 hour 15 minutes
\end{itemize}

\vspace{1cm}

\textbf{INSTRUCTIONS}
\begin{itemize}
\item Use black ink or ball-point pen.
\item Answer all questions.
\item Read each question carefully before answering.
\item Show all your working.
\item Do not write in the margins.
\end{itemize}

\textbf{INFORMATION}
\begin{itemize}
\item The total number of marks for this paper is 40.
\item The marks for each question are shown in brackets.
\item You are expected to use a calculator where appropriate.
\end{itemize}
\end{center}

\newpage

\begin{center}
{\Large \textbf{Section A: Software Development}}
\end{center}

\begin{enumerate}
\item Define the term \textit{software development methodology}. [2 marks]

\item Compare and contrast two different software development methodologies: Waterfall and Agile. [6 marks]

\item A small software company is developing a mobile application for tracking fitness activities. 
    \begin{enumerate}[label=(\alph*)]
    \item Explain why prototyping might be an appropriate methodology for this project. [4 marks]
    \item Describe two potential risks in the software development process for this application. [4 marks]
    \end{enumerate}

\item Discuss the importance of testing in the software development lifecycle. Include different types of testing and their purposes. [8 marks]

\item Explain how version control systems support collaborative software development. Provide specific examples of how they can help manage code changes. [6 marks]

\item Describe the key stages of the software development lifecycle, explaining the purpose of each stage. [10 marks]
\end{enumerate}

\newpage

\begin{center}
\textbf{GRADE BOUNDARIES}
\begin{tabular}{|c|c|}
\hline
Grade & Mark Range \\
\hline
A* & 36-40 \\
A & 32-35 \\
B & 28-31 \\
C & 24-27 \\
D & 20-23 \\
E & 16-19 \\
\end{tabular}
\end{center}

\end{document}
```