
\documentclass{article}
\usepackage{amsmath,amssymb,graphicx,hyperref,listings,xcolor}
\usepackage[a4paper,margin=1in]{geometry}

\title{1.1 The characteristics of contemporary processors, input, output and storage devices}
\author{APOLLO AI}
\date{\today}

\begin{document}
\maketitle

```latex
\documentclass{article}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumitem}

\geometry{a4paper, margin=1in}

\title{OCR A-Level Computer Science \\ Unit 1.1 Practice Assessment \\ Processor Characteristics, Input, Output and Storage Devices}
\date{}

\begin{document}

\maketitle

\section*{Examination Instructions}
\begin{itemize}
    \item Time allowed: 1 hour
    \item Total marks: 40 marks
    \item Answer \textbf{ALL} questions
    \item Write clearly in black ink
    \item Show all your working
\end{itemize}

\section*{Grade Boundaries}
\begin{tabular}{|l|c|}
    \hline
    Grade & Marks Required \\
    \hline
    A* & 36-40 \\
    A & 32-35 \\
    B & 28-31 \\
    C & 24-27 \\
    D & 20-23 \\
    E & 16-19 \\
    \hline
\end{tabular}

\section*{Questions}

\subsection*{Question 1 \textbf{[6 marks]}}
Explain the difference between CISC and RISC processor architectures. Provide two specific examples to support your explanation.

\subsection*{Question 2 \textbf{[8 marks]}}
Describe the process of how a CPU fetches, decodes, and executes an instruction using the fetch-decode-execute cycle. Include a detailed explanation of the role of the program counter and memory address register in this process.

\subsection*{Question 3 \textbf{[6 marks]}}
Compare and contrast the characteristics of different types of computer memory:
\begin{itemize}
    \item Cache memory
    \item RAM
    \item ROM
\end{itemize}
Discuss their speed, volatility, and typical uses in a computer system.

\subsection*{Question 4 \textbf{[10 marks]}}
A computer manufacturer is designing a new processor for high-performance computing. 
\begin{enumerate}[label=(\alph*)]
    \item Explain how pipelining can improve processor performance. \textbf{[4 marks]}
    \item Discuss two potential limitations or challenges of pipelining. \textbf{[6 marks]}
\end{enumerate}

\subsection*{Question 5 \textbf{[10 marks]}}
Evaluate the impact of multicore processors on modern computing:
\begin{enumerate}[label=(\alph*)]
    \item Explain how multicore processors improve computational efficiency. \textbf{[4 marks]}
    \item Discuss the challenges of developing software to fully utilize multicore processors. \textbf{[6 marks]}
\end{enumerate}

\vfill
\begin{center}
\textbf{END OF QUESTION PAPER}
\end{center}

\end{document}
```

\end{document}
