\documentclass{article}
\usepackage{amsmath,amssymb,graphicx,enumitem}
\usepackage[margin=1in]{geometry}

\title{OCR A-Level Computer Science}
\subtitle{H446/01: Computer Systems}
\author{Topic 1.1: The characteristics of contemporary processors, input, output and storage devices}
\date{}

\begin{document}

\maketitle

\section*{Instructions to Candidates}
\begin{itemize}
    \item Answer ALL questions.
    \item Write your answers in the spaces provided.
    \item The total mark for this paper is 50.
    \item The marks for each question are shown in brackets [ ].
\end{itemize}

\vspace{1cm}

\begin{enumerate}

\item Define the following components of the CPU:
\begin{enumerate}[label=(\alph*)]
    \item Control Unit [2 marks]
    \item Arithmetic Logic Unit [2 marks]
\end{enumerate}

\item Explain the function of the following registers in the fetch-decode-execute cycle:
\begin{enumerate}[label=(\alph*)]
    \item Program Counter (PC) [2 marks]
    \item Memory Address Register (MAR) [2 marks]
    \item Memory Data Register (MDR) [2 marks]
    \item Current Instruction Register (CIR) [2 marks]
\end{enumerate}

\item Describe the fetch-decode-execute cycle with reference to the registers mentioned in question 2. [6 marks]

\item Compare and contrast CISC and RISC processors. Your answer should include:
\begin{enumerate}[label=(\alph*)]
    \item Three differences between CISC and RISC architectures [6 marks]
    \item One advantage and one disadvantage of each architecture [4 marks]
\end{enumerate}

\item Explain what is meant by each of the following, and how they affect processor performance:
\begin{enumerate}[label=(\alph*)]
    \item Clock speed [2 marks]
    \item Number of cores [2 marks]
    \item Cache [2 marks]
\end{enumerate}

\item Describe the differences between the Von Neumann and Harvard architectures. [4 marks]

\item Explain how pipelining improves processor performance. [4 marks]

\item A computer system has the following specification:
\begin{itemize}
    \item 3.2 GHz quad-core processor
    \item 8 GB DDR4 RAM
    \item 512 GB SSD
    \item 2 TB HDD
\end{itemize}

\begin{enumerate}[label=(\alph*)]
    \item Explain what is meant by a quad-core processor. [2 marks]
    \item Compare the characteristics of the SSD and HDD in this system. [4 marks]
\end{enumerate}

\item Explain the difference between serial and parallel data transmission, including an example of where each might be used. [4 marks]

\end{enumerate}

\newpage

\section*{Grade Boundaries}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
A* & A & B & C & D & E \\
\hline
45-50 & 40-44 & 35-39 & 30-34 & 25-29 & 20-24 \\
\hline
\end{tabular}
\end{center}

\end{document}