You haven't asked me any specific questions in our conversation yet. You've just set up the context for our discussion about OCR A-Level Computer Science Topic 1.1 (The characteristics of contemporary processors, input, output and storage devices) and requested to be in TEST mode.

I'll create a mock exam paper on this topic for you to practice with:

```latex
\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{OCR A-Level Computer Science}
\author{Mock Examination}
\date{Topic 1.1: The characteristics of contemporary processors, input, output and storage devices}

\begin{document}

\maketitle

\section*{Instructions to Candidates}
\begin{itemize}
    \item Answer ALL questions.
    \item Write your answers in the spaces provided.
    \item Total marks available: 50
    \item Time allowed: 60 minutes
\end{itemize}

\section*{Grade Boundaries}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
A* & A & B & C & D & E \\
\hline
45 & 40 & 35 & 30 & 25 & 20 \\
\hline
\end{tabular}
\end{center}

\vspace{1cm}

\begin{enumerate}

\item Define the term 'clock speed' and explain how it affects processor performance. [3 marks]

\item 
\begin{enumerate}[label=(\alph*)]
    \item What is meant by the term 'core' in a multi-core processor? [1 mark]
    \item Explain two benefits of multi-core processing. [4 marks]
\end{enumerate}

\item Explain the difference between CISC and RISC processor architectures. [4 marks]

\item 
\begin{enumerate}[label=(\alph*)]
    \item What is pipelining in processor design? [2 marks]
    \item Explain how pipelining improves processor performance. [3 marks]
\end{enumerate}

\item 
\begin{enumerate}[label=(\alph*)]
    \item Describe the Von Neumann architecture. [3 marks]
    \item Explain one limitation of the Von Neumann architecture. [2 marks]
\end{enumerate}

\item Explain the role of the following components in a processor:
\begin{enumerate}[label=(\alph*)]
    \item Control Unit [2 marks]
    \item ALU (Arithmetic Logic Unit) [2 marks]
    \item Registers [2 marks]
\end{enumerate}

\item 
\begin{enumerate}[label=(\alph*)]
    \item What is cache memory? [2 marks]
    \item Explain the purpose of L1, L2, and L3 cache in modern processors. [3 marks]
\end{enumerate}

\item A computer has a processor with a clock speed of 3.2 GHz.
\begin{enumerate}[label=(\alph*)]
    \item Calculate how many cycles this processor can execute in one second. [1 mark]
    \item If an instruction takes 4 clock cycles to complete, calculate how many of these instructions the processor can execute per second. [2 marks]
\end{enumerate}

\item Explain the difference between optical, magnetic and solid-state storage devices, giving one example of each. [6 marks]

\item 
\begin{enumerate}[label=(\alph*)]
    \item Define the terms 'input device' and 'output device'. [2 marks]
    \item For each of the following scenarios, recommend a suitable input or output device and justify your choice: [6 marks]
    \begin{enumerate}[label=(\roman*)]
        \item A visually impaired user needs to interact with a computer
        \item A graphic designer creating detailed artwork
        \item A warehouse tracking inventory
    \end{enumerate}
\end{enumerate}

\item Explain the concept of embedded systems and give two examples of embedded systems used in everyday life. [4 marks]

\end{enumerate}

\end{document}
```

Would you like to attempt this mock exam paper? Or would you prefer a different learning approach to explore this topic?