```latex
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}

\geometry{a4paper, margin=2cm}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{Page \thepage}

\begin{document}

% First Page - Exam Cover Sheet
\begin{center}
{\large\textbf{OCR A-LEVEL COMPUTER SCIENCE}}

\vspace{1cm}

{\Large\textbf{H446/01 Computer Systems}}

\vspace{1cm}

\begin{tabular}{|p{0.45\textwidth}|p{0.45\textwidth}|}
\hline
Centre Number & Candidate Number \\
\rule{0pt}{1cm} & \rule{0pt}{1cm} \\
\hline
\end{tabular}

\vspace{1cm}

\begin{tabular}{|p{0.9\textwidth}|}
\hline
Surname \rule{0pt}{1cm} \\
\hline
Forename(s) \rule{0pt}{1cm} \\
\hline
Candidate Signature \rule{0pt}{1cm} \\
\hline
\end{tabular}

\vspace{1cm}

\begin{tabular}{|l|l|}
\hline
Paper Reference & H446/01 \\
\hline
Total Marks & 40 \\
\hline
Time Allowed & 1 hour 30 minutes \\
\hline
\end{tabular}

\vspace{1cm}

\textbf{INSTRUCTIONS}
\begin{itemize}
\item Use black ink or ball-point pen.
\item Answer all questions.
\item Show clearly how you obtain your answers.
\item You may use a calculator.
\end{itemize}

\textbf{INFORMATION}
\begin{itemize}
\item The total number of marks for this paper is 40.
\item The marks for each question are shown in brackets.
\item Quality of written communication will be assessed in some questions.
\end{itemize}
\end{center}

\newpage

% Actual Exam Questions
\begin{center}
{\Large\textbf{Section A: Software and Software Development}}
\end{center}

\section*{Answer ALL questions}

\begin{enumerate}
\item Define the term \textit{firmware} and explain its purpose in computer systems. [4 marks]

\item Compare and contrast \textbf{proprietary software} and \textbf{open-source software}, discussing three key differences. [6 marks]

\item Explain the stages of the \textbf{software development lifecycle (SDLC)} and discuss why each stage is crucial in producing high-quality software. [10 marks]

\item Describe two different types of software licensing models and evaluate their advantages and disadvantages for software developers. [8 marks]

\item Discuss the ethical considerations surrounding software development, including:
\begin{itemize}
\item Privacy protection
\item Data security
\item Potential misuse of software technologies
\end{itemize}
Provide specific examples to support your discussion. [12 marks]
\end{enumerate}

\vspace{1cm}

\begin{center}
\textbf{END OF QUESTION PAPER}
\end{center}

\newpage

% Grade Boundaries
\begin{center}
{\Large\textbf{Grade Boundaries}}

\begin{tabular}{|c|c|c|}
\hline
Grade & Raw Mark Range & Percentage \\
\hline
A* & 36-40 & 90-100\% \\
A & 32-35 & 80-89\% \\
B & 28-31 & 70-79\% \\
C & 24-27 & 60-69\% \\
D & 20-23 & 50-59\% \\
E & 16-19 & 40-49\% \\
U & 0-15 & 0-39\% \\
\hline
\end{tabular}
\end{center}

\end{document}
```